Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-02-14 manuscript/phylogenetic_signal_manuscript.tex
still going through comments

  We calculated niche overlap for each pair of species within
  a community using a modified Jaccard index. The 
  Jaccard index $J_{ij}$ describes the proportion of shared interaction 
  partners for for species $i$ and $j$ and is defined as:

  \begin{equation}
    J_{ij} = \frac{M_{ij}}{P_i+P_j-M_ij} ,,
  \end{equation}

  where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
  species $i$ and $j$ and $P_i$ and $P_j$ are the sets of interaction 
  \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
  weight to species sharing a large number of interaction partners as well as 
  those sharing a large proportion (i.e., to emphasize pairs of generalists 
  sharing most of their interaction partners over specialists sharing a single 
  interaction partner). We therefore recorded, for each species, the number of 
  shared interaction partners $M_{ij}$ and the number of interaction partners 
  that were not shared ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a 
  single index $J_{ij}$ we therefore defined niche overlap between species
  $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).

@@

  We modelled the relationship between niche overlap and phylogenetic distance
  using a logistic regression. We used both the numbers of shared and 
  non-shared partners as dependent variables and centred, scaled phylogenetic 
  distance as the independent variable. This is conceptually similar to 
  modelling successes and failures in a binomial-distributed process. 
  Accordingly, we assumed a binomial distribution for residuals. All regressions were fit using the R~\citep{R} function 
  ``glm'' from package \emph{lme4}~\citep{lme4}. To avoid potential 
  confounding effects of different relationships in different networks, we 
  modelled the relationship between overlap and phylogenetic distance within 
  each network separately.

  Note that pairs of plants are not always independent: the same plant will
  appear in many pairs. This violates the assumption of independence used when 
  calculating the significance of logistic regressions within the R~\citep{R} 
  package \emph{lme4}~\citep{lme4}. To calculate significance of the 
  relationships we observed, it was therefore necessary to compare the 
  observed relationships to those in a suite of random networks. To create 
  these networks, we shuffled interactions among species while preserving row 
  and column totals. That is, each species retained the same number of 
  interaction partners as in the observed network but the exact set of 
  partners (and therefore niche overlaps with all other species) varied across 
  random networks. We preserved the observed phylogenetic relationships 
  between species in all cases. For each observed network, we created 999 such 
  random networks and calculated the relationship between niche overlap and 
  phylogenetic distance. This gave us a null distribution for each observed 
  network with which to determine the significance of the observed 
  relationship.

  This randomization approach also allows us to estimate type I and type II 
  error for our analysis. To do this, we created 500 randomizations of each 
  random network and, again keeping the observed phylogenetic distances 
  between plant species, repeated our analyses. We can then determine the 
  number of randomized networks which appear to have significant 
  overlap-phylogenetic distance relationships relative to the randomizations 
  of these random networks (type I error). [[How does this get at type II error?]]

@@

    [[Reviewers demanded this - it seems very boring]]
    Comparing the results in the observed networks to those obtained after randomising phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the random networks (Fig.~\ref{obs_vs_random}). Observed networks with a negative relationship between phylogenetic distance and overlap always had a more negative slope than that obtained from the random networks, while the 10 networks with positive relationships between phylogenetic distance and overlap always had more positive relationships than the random networks.

    Comparing the random networks to randomizations of the random networks, the slope obtained from the initial random network was quite variable with respect to the slopes obtained from 500 randomizations of the random network. Averaged over the 1000 randomizations of each observed network, the slope of the random network was more extreme than 48.1-51.3\% of the randomizations of the random network. This confirms that shuffling phylogenetic distances between plant pairs destroys the relationship between distance and interaction partner overlap, and that further shuffling distances does not have a predictable effect.

>>>>

  We calculated niche overlap for each pair of species within a community 
  using a Jaccard index to describe the number of shared interaction 
  partners, augmented with the number of interaction partners which were 
  not shared. The Jaccard index $J_{ij}$ describes the proportion of 
  shared interaction partners for for species $i$ and $j$ and is defined as:

  \begin{equation}
    J_{ij} = \frac{M_{ij}}{P_i+P_j-M_{ij}} ,
  \end{equation}

  where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners of 
  species $i$ and $j$ and $P_i$ and $P_j$ are the sizes of the sets of interaction 
  \emph{partners} for species $i$ and $j$ respectively. We wished to give more 
  weight to species sharing a large number of interaction partners as well as 
  those sharing a large proportion (i.e., to emphasize pairs of generalists 
  sharing most of their interaction partners over specialists sharing a single 
  interaction partner). We therefore recorded, for each species, the number of 
  shared interaction partners $M_{ij}$ and the number of interaction partners 
  for each species pair that were not shared 
  ($U_{ij}$ = $P_{i}$+$P_{j}$-2$M_{ij}$). Instead of a single index $J_{ij}$ 
  we therefore keep track of the information needed to compute
  niche between species $i$ and $j$ as a tuple: ($M_{ij}$, $U_{ij}$).

@@

  We modelled the relationship between niche overlap and phylogenetic distance
  using a logistic regression. We used both the numbers of shared ($M_{ij}$)and 
  non-shared ($U_{ij}$) partners as dependent variables and centred, scaled phylogenetic 
  distance as the independent variable. This approach is conceptually similar to 
  modelling successes and failures in a binomial-distributed process. 
  Accordingly, we assumed a binomial distribution for residuals. Regressions of
  niche overlap and phylogenetic distance within each network were fit using the
  R~\citep{R} base function ``glm''. These separate regressions avoid the potential
  for confounding the effects of different relationships in different networks. As
  we also wished to evaluate the overall trend across networks, we fit an additional
  regression of niche overlap and phylogenetic distance across all network types.
  As well as the fixed effect of phylogenetic distance, this regression included 
  fixed effects of network type (pollination or herbivory) and the interaction 
  between phylogenetic network type and random intercepts and slopes per network.
  This expanded regression was fit using the R~\citep{R} function ``glmer'' from
  package \emph{lme4}~\citep{lme4}. [[Confirm that I actually use the separate 
  regressions and not just the full one. ]]

  Note that pairs of plants are not always independent: the same plant will
  appear in many pairs. This violates the assumption of independence used when 
  calculating the significance of logistic regressions within the R~\citep{R} 
  base package or the package \emph{lme4}~\citep{lme4}. To calculate significance 
  of the regression coefficients we observed, it was therefore necessary to compare the 
  observed relationships to those in a suite of appropriately permuted networks. To create 
  these networks, we shuffled interactions among species while preserving row 
  and column totals. That is, each species retained the same number of 
  interaction partners as in the observed network but the exact set of 
  partners (and therefore niche overlaps with all other species) varied across 
  permuted networks. We preserved the observed phylogenetic relationships 
  between species in all cases. For each observed network, we created 999 such 
  permuted networks and calculated the relationship between niche overlap and 
  phylogenetic distance. This gave us a null distribution for each observed 
  network with which to determine the significance of the observed 
  relationship.

  This permutation approach also allows us to estimate type I and type II 
  error for our analysis. To do this, we created 500 permutations of each 
  permuted network and, again keeping the observed phylogenetic distances 
  between plant species, repeated our analyses. We can then determine the 
  number of permuted networks which appear to have significant 
  overlap-phylogenetic distance relationships relative to the permutations 
  of these permuted networks (type I error). [[How does this get at type II error?]]

@@

    [[Reviewers demanded this - it seems very boring]]
    Comparing the results in the observed networks to those obtained after permuting phylogenetic distances across pairs of plants, the observed slope of the relationship between phylogenetic distance and interaction partner overlap was always more extreme (i.e., always lesser or always greater) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}). Observed networks with a negative relationship between phylogenetic distance and overlap always had a more negative slope than that obtained from the permuted networks, while the 10 networks with positive relationships between phylogenetic distance and overlap always had more positive relationships than the permuted networks.

    Comparing the permuted networks to permutations of the permuted networks, the slope obtained from the initial permuted network was quite variable with respect to the slopes obtained from 500 permutationss of the permuted network. Averaged over the 1000 permutations of each observed network, the slope of the permuted network was more extreme than 48.1-51.3\% of the permutations of the permuted network. This confirms that shuffling phylogenetic distances between plant pairs destroys the relationship between distance and interaction partner overlap, and that further shuffling distances does not have a predictable effect.
